### 2021-04-17 manuscript.rmd
maintain consistency

Comparative research in journalism studies, unlike randomized surveys or randomized media experiments, usually collects all available data. In contrast to sampling, these studies are actually doing census of all data and there is no way to get more data unless the scope of these studies is changed [@berk:1995:SIA]. It is especially true for modern large-N studies using automated content analytic techniques. @burggraaff:2017:T, for instance, "collected all available news items from a selection of major Dutch news outlets, both online and print" (p. 6) and that amounted to 762,095 articles from 9 outlets in the period of 2014-2015.

@@

We excluded media outlets that contributed <1000 articles in that year. This threshold allowed us to retain media outlets that the frequency of China coverage can be reliably estimated. In total, 61 media outlets from Spain (n = 11), Romania (n = 11), US (n = 7), Austria (n = 6), Germany (n = 5), Norway (n = 5), Australia (n  = 4), Brazil (n = 4), UK (n = 4), South Korea (n = 2), and the Netherlands (n = 2) were included. These 61 media outlets contributed 1,525,871 articles.

@@

Bayesian multilevel regression analysis is also useful to study temporal changes, because observations from the same subject collected from different time points are naturally a cluster. The same strategy for handling the clustering of observations in the multilevel modeling can be used. We model observations from the same media outlet are nested within the media outlet and then the media outlet is nested within its countries. Suppose we would like to study if there is a systematic increase in $z$ across all outlets, maybe due to the COVID-19 pandemic and the presidential election in the US. It can be analyzed with this 3-level model.

@@

The regression coefficient for the year dummy variable is 0.49 (95\% HDI 0.38, 0.60). It seems that there is a global increase in China coverage from 2019 to 2020.

@@

In this paper, we argue the case for using Bayesian multilevel regression analysis to analyze data from comparative communication research. We demonstrate using the openly available useNews dataset that Bayesian analysis provides valid inference of ecological effects and can be done easily with the R package *brms*. Using a Bayesian approach, however, has also clearly some disadvantages. Researchers have to define priors in order to run a Bayesian regression analysis. As we could show this limitation does not pose a controversial challenge as weakly informative priors can be chosen and in most cases enough data is available and thus the priors have almost no influence on the posterior distribution of the parameters. If we have prior knowledge it allows us to create even better models. Furthermore, it takes more time to get the results of a Bayesian regression analysis. Estimating a Bayesian regression model is a computationally demanding task. It took 4 days on a regular computer to get the results of the Bayesian regression model with 1,525,871 articles (Model B1). Still, eventually it worked and typical studies in comparative journalism research [e.g. 6525 articles in @esser:2013:C] can be estimated in a reasonable time frame [^TIME].

>>>>

Comparative research in journalism studies, unlike randomized surveys or randomized media experiments, usually collects all available data. In contrast to sampling, these studies are actually doing census of all data and there is no way to get more data unless the scope of these studies is changed [@berk:1995:SIA]. It is especially true for modern large-N studies using automated content analytic techniques. @burggraaff:2017:T, for instance, "collected all available news items from a selection of major Dutch news outlets, both online and print" (p. 6) and that amounted to 762,095 articles from 9 outlets in the period of 2014--2015.

@@

We excluded media outlets that contributed <1,000 articles in that year. This threshold allowed us to retain media outlets that the frequency of China coverage can be reliably estimated. In total, 61 media outlets from Spain (n = 11), Romania (n = 11), US (n = 7), Austria (n = 6), Germany (n = 5), Norway (n = 5), Australia (n  = 4), Brazil (n = 4), UK (n = 4), South Korea (n = 2), and the Netherlands (n = 2) were included. These 61 media outlets contributed 1,525,871 articles.

@@

Bayesian multilevel regression analysis is also useful to study temporal changes, because observations from the same subject collected from different time points are naturally a cluster. The same strategy for handling the clustering of observations in the multilevel modeling can be used. We model observations from the same media outlet are nested within the media outlet and then the media outlet is nested within its countries. Suppose we would like to study if there is a systematic increase in $z$ across all outlets, maybe due to the COVID-19 pandemic and the presidential election in the US. It can be analyzed with this three-level model.

@@

The regression coefficient for the year dummy variable is 0.49 (95\% HDI 0.38, 0.60). There is a global increase in China coverage from 2019 to 2020.

@@

In this paper, we argue the case for using Bayesian multilevel regression analysis to analyze data from comparative communication research. We demonstrate using the openly available useNews dataset that Bayesian analysis provides valid inference of ecological effects and can be done easily with the R package *brms*. Using a Bayesian approach, however, has also clearly some disadvantages. Researchers have to define priors in order to run a Bayesian regression analysis. As we could show this limitation does not pose a controversial challenge as weakly informative priors can be chosen and in most cases enough data is available and thus the priors have almost no influence on the posterior distribution of the parameters. If we have prior knowledge it allows us to create even better models. Furthermore, it takes more time to get the results of a Bayesian regression analysis. Estimating a Bayesian regression model is a computationally demanding task. It took 4 days on a regular computer to get the results of the Bayesian regression model with 1,525,871 articles (Model B1). Still, eventually it worked and typical studies in comparative journalism research [e.g. 6,525 articles in @esser:2013:C] can be estimated in a reasonable time frame [^TIME].
